### 2019-07-04 manuscript.tex
Update manuscript.tex

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. (and BoylMcMo02)

Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15}, is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15} and a key approach in comprehending and intervening the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13}.  FGC practice is often analyzed using social norm constructs \cite{DuncWand11, EffeVogt15, Hayf05, Youn02, } (more cite{BoylCorl010, Drol11, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm)).  For example, convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}

Although convention theory was well deliberated and applied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges \cite{EffeVogt15} and multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13}.

% norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}

% prevalence of FGC in those 4 nations.

@@

Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} (and Bicc etc, more).  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices (i.e., cutting daughters’s genitals).  The main norm theory we tested in this paper was that women’s intention on genital cutting of their daughters was dependent on other women’s intention on cutting their daughters in their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

@@

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 1/09/19).

Only women with daughters to be considered for FGC were included in main model (the daughter model) and the mixed structure (future-daughter) model, while the future model included all the women in the samples; we included only women who had daughters yet to be considered FGC in the models to analyze intention of fgc behaviour.  All woman were included in the future model.  As a result,  there were xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
\cfonly{\cite{Rima08}}*

Our main interest in this study is to analyze how norms associate with behavioural intention.  We focus on whether women will likely genitally cut their daughters based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g. women’s own FGC status).  Therefore, our main response variables were woman's behavioural intention to cut their daughters genital in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.  In other words, only women with daughter for a consideration of fgc were included in the main and mix models, and all women were included in the persistence model.  The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.  The main predictors were woman's FGC status and beliefs of FGC benefits.  Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use, gender awareness (see — for questions of gender awareness proxy) and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}

@@

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}
\cfcmt{Do we explain conveyance of uncertainty and data sampling?}

@@

\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing? }
\cfcmt{reference: Methods and the first paragraph of Discussion\cite{Chia14}}

@@

>>>>

The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and norms attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.

Social norm is often used to understand behavioural pattern of FGC \cfonly{more cite{BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17, Youn02} (to confirm)}.  Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.  Convention theory, a widely inferred approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC is also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.

Although convention theory was well deliberated and applied and showed a larger effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.  Multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}

In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitude on the practice.  Besides social norms of FGC, women’s gender values and their social environment were also incorporated.

@@

This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices.  Our main interest in this study is to analyze how norms associate with behavioural intention.  We focus on whether women will likely genitally cut their daughters based on their current intention and that provides a relatively more detailed result on how FGC norms interacts FGC practice than using than what had already happened (e.g. women’s own FGC status).  The main norm theory tested in this paper was that women’s intention on practicing FGC on their daughters was dependent on other women’s intention on cutting their daughters within their community.  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to have their daughters undergoing FGC in order to understand if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “daugher_ persistence” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of genitally cutting daughters to understand how such positions change the main model.

@@

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx and xxx  respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}

\cfonly{\cite{Rima08}}*

Our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  The predictors selected based on literature (e.g., aforementioned above) were woman's FGC status and beliefs of FGC benefits (see supp for a list of questionnaire of FGC benefits).  The beliefs of FGC benefits were quantified using average score \cf{pls confirm} to identify the strength of benefits associating with fgc practice. We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?}.  Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}

\jdcmt{Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess.} \cfcmt{Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  But as J said, it is too hard! } %``explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. `` \cite{Hayf05}
\cfcmt{Bayesian model \cite{KandNwak09} ``Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788)}
\cfcmt{Regarding FGC benefits modules, there were 9 questions.  Keya had all the 9, Mali and SL 7 (missing promiscuity and STD), NG 8, missing STD).  Should we drop STD since 3 out of 4 missed this variable?}
\cfonly {in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).

@@

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfjdml{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}

\cfcmt{Do we explain conveyance of uncertainty and data sampling?}

@@

\cfcmt{Do we do any within-community variation and between-community variation?  Is it a thing? }

\cfonly{reference: Methods and the first paragraph of Discussion\cite{Chia14}}

@@

=====stop reading===
